Double Elimination Tournament

### 2025-02-20 double_elimination.qmd

  # Remove ties if ties = FALSE
  if (!ties) {
    final_results <- final_results %>%
      filter(!is.na(true_rank)) %>%
      arrange(rank_hat) %>%
      mutate(rank_hat = rank(rank_hat, ties.method = "random"))
  }
  else{
    final_results <- final_results %>%
      filter(!is.na(true_rank)) %>%
      arrange(rank_hat) %>%
      mutate(rank_hat = rank(rank_hat, ties.method = "average"))
  }

@@

test <- simulate_double_elimination_tournament(num_teams = 8, distribution = "Normal", ties=F, series=1)
test
#manual_test <- simulate_double_elimination_tournament(num_teams = 4, distribution = "Manual", ties=F, series=1)
#manual_test

>>>>

  # Remove ties if ties = FALSE
  if (!ties) {
    final_results <- final_results %>%
      filter(!is.na(true_rank)) %>%
      arrange(true_rank) %>%
      mutate(rank_hat = rank(rank_hat, ties.method = "first"))
  }
  else{
    final_results <- final_results %>%
      filter(!is.na(true_rank)) %>%
      arrange(rank_hat) %>%
      mutate(rank_hat = rank(rank_hat, ties.method = "average"))
  }

@@

#test <- simulate_double_elimination_tournament(num_teams = 8, distribution = "Normal", ties=F, series=1)
#test
#manual_test <- simulate_double_elimination_tournament(num_teams = 4, distribution = "Manual", ties=F, series=1)
#manual_test

# Gets all results of a normal distribution num_teams between 4 and 64 single-game elimination
de_norm_results <- list()
for (teams in c(4,8,16,32,64)) {
  de_norm_results[[as.character(teams)]] <- list()
  for (replicate in 1:10000) {
    # Store each simulation result in the list with unique indexing
    de_norm_results[[as.character(teams)]][[replicate]] <- simulate_double_elimination_tournament(
      num_teams = teams,
      distribution = "Normal",
      ties = FALSE,
      series = 1
    )
  }
}

de_norm_results <- do.call(rbind, lapply(names(all_normal_results), function(teams) {
  team_results <- do.call(rbind, all_normal_results[[teams]])
  team_results$teams <- as.numeric(teams)
  return(team_results)
}))
de_norm_results
